Soss

### 2019-12-31 paper/paper.tex
edits

\author{Chad Scherrer}
\orcid{0000-0002-1490-0304}
\affiliation{%
  \institution{RelationalAI}
  % \department{Department of Brain and Cognitive Sciences}
  %\streetaddress{43 Vassar St}
  %\city{Cambridge}
  %\state{MA}
  %\postcode{02139}
  %\country{USA}
}
\email{chad.scherrer@gmail.com}

@@

\begin{itemize}
    \item Model specification in Soss is \emph{declarative}; statements are ordered not by the order entered by the user, but by the partial order given by their variable dependencies.
    \item Soss models are \emph{first-class}; models can be passed as arguments to other models, or used in place of distributions within a model.
    \item Values and distributions in Soss are represented internally as \emph{abstract syntax trees}, maximizing the flexibility of available inference methods.
    \item Code generation \texttt{GeneralizedGenerated.jl}
    \item Model transformations
    \item Function-like models
    \item Symbolic simplification
    \item Extensibility
\end{itemize}

>>>>

\author{Chad Scherrer}
\orcid{0000-0002-1490-0304}
\affiliation{%
  \institution{RelationalAI}
  % \department{Department of Brain and Cognitive Sciences}
  %\streetaddress{43 Vassar St}
  \city{Seattle}
  \state{WA}
  %\postcode{02139}
  %\country{USA}
}
\email{chad.scherrer@gmail.com}

@@

\begin{itemize}
    \item Model specification in Soss is \emph{declarative}; statements are ordered not by the order entered by the user, but by the partial order given by their variable dependencies.
    \item Soss models are \emph{first-class}; models can be passed as arguments to other models, or used in place of distributions within a model.
    \item Soss models are \emph{function-like}; abstractly, a model may be considered a function from its arguments to a joint distribution. In particular, specification of ``observed variables'' is separated from model definition.
    \item Values and distributions in Soss are represented internally as \emph{abstract syntax trees}, maximizing the flexibility of available inference methods.
    \item Soss uses \emph{staged compilation} for inference primitives like \jl#rand# and \jl#logpdf#, via novel \emph{generalized generated functions} from \texttt{GeneralizedGenerated.jl}.
    \item Model transformations
    \item Symbolic simplification
    \item Extensibility
\end{itemize}

Finally, Soss addresses the age-old challenge of naming things in computer science via Cockney rhyming slang (``sauce pan'' rhymes with ``Stan''). {\bf S}oss is {\bf o}pen-{\bf s}ource {\bf s}oftware.
